### 2016-02-21 experiments.tex
another small fix

In one sense, the discovery curve improvements here are practically useful, but not spectacular.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very best curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank competing curves, so this is not a practical approach to fuzzer taming.  The best methods for different subjects in previous work varied widely, even in such peculiar ways as less-fine-grained coverage providing better results in some cases, worse in other cases.   In practice, previous work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, and included methods such as comparing output signatures that are inapplicable to many settings.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.

>>>>

In one sense, the discovery curve improvements here are practically useful, but not spectacular.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very best curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank competing curves, so this is not a practical approach to fuzzer taming.  The best methods for different subjects in previous work varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, previous work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential properties.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.
